---
title: "Cabbages"
author: "Alexis Velasco"
date: "5/31/22"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
plot(VitC~Cult,data=veggy)
```

The median for c39 is about 50 which has a higher median then c52 which has a median around 70. The difference in median between c39 and c52 can be seen by the two boxes being so far apart that they would not cross each other if they were to merge together. 


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

The median amount for c39 is 51 where  the median for c52 is at 64.5. c52 is seen to have a higher amount of VitC by averaging 13.5 more points in the median statement. It can also be seen that the c52 min is 6 points higher than c39.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
 The chances fo getting these results are .00000003405 if there was no difference between the two.
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The c52 has a higher 50 percent then the c39 percentile.The median amount for c39 is 51 where the median for c52 is at 64.5. Having a higher amount of VitC by averaging 13.5 more points in the median statement.It can be seen that the c52 min is 6 points higher than c39 showing c52 has more VitC to begin with. The possibility of a difference in these results would be .00000003405.
